The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-10 analysis/paper/paper.qmd
Update code chunk names

```{r ngrams}
#| dependson: clean-text

@@

@@

```{r}
## Bigram tf-idf
bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

@@

```{r}
## Trigram tf-idf
trigram_tf_idf <- emu_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

>>>>

```{r bigrams}

@@

```{r trigrams}

@@

```{r bigram-tfidf}
## Bigram tf-idf
bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

@@

```{r trigram-tfidf}
## Trigram tf-idf
trigram_tf_idf <- emu_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))
